%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.75in,right=0.6in,bottom=0.75in]{geometry} % Document margins
\usepackage[hidelinks]{hyperref}
\urlstyle{same}

\name{Christopher C. Stoafer} % Your name
\address{23-51 38th St. Apt. D3 \\ Astoria, NY 11105} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(415)$\, \cdot \,$203$\, \cdot \,$2855 \\ cstoafer@gmail.com \\ \url{www.chrisstoafer.com} \\ GitHub: cstoafer} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	Career Profile SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Career Profile}
%
%Highly technical graduate student with experience in experimentation, consulting, and analysis seeking a technical position in data-driven technologies.  Strengths include analytical, data related software development, 
%
%\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Columbia University}, Graduate School of Arts and Sciences \hfill {\em New York, NY, 2010-2015} \\ 
Ph.D. in Applied Physics \hfill {\em  Plasma Physics and Nuclear Fusion} \\
M.S. in Applied Physics \hfill {\em GPA: 3.8/4.0} \smallskip 

{\bf California Polytechnic State University } \hfill {\em San Luis Obispo, CA, 2003-2008} \\ 
B.S. in Chemistry and Biochemistry \hfill {\em Graduated Magna cum Laude} \\
Minor in Physics \hfill {\em GPA: 3.8/4.0} \smallskip

%\emph{Data Science Coursework:} 

%\begin{tabular}{ @{} >{}l @{\hspace{8ex}} l @{\hspace{8ex}} l }% @{\hspace{4ex}} l @{\hspace{4ex}} l }
%Machine Learning & Advanced Programming & Introduction to Data Science \\
%Modeling Social Data & Algorithms \\
%\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH AND PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research and Professional Experience}

\begin{rSubsection}{Capital One Labs}{July, 2015 - Present}{Senior Data Scientist}{New York, NY}
\item As a data science lead, engage with a team in Small Business Credit Card to explore, ingest, and combine public and external data sources with internal data, driving data enrichment of small business entities.  %Regularly engage with senior leadership to iteratively prioritize tasks that optimize business value.
\item Designed and implemented an unsupervised model to detect anomalous spending and payment behavior of small businesses using Python and scikit-learn.
\item Managed a team in developing an internal text mining and natural language processing package in Python, promoting a generalized toolkit and text mining community across Capital One.
\item Promoted from Senior Associate to Principal Associate in July, 2016.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Columbia University Plasma Lab}{August, 2010 - July, 2015}{Graduate Research Student}{New York, NY}
\item Formulated and conducted experiments related to the study of plasma physics and nuclear fusion.  
\item Improved and developed data analysis algorithms in Python used by the entire lab for understanding plasma conditions by interpreting several diagnostic measurements. %Techniques include Fourier analysis, signal correlations and convolutions, and high/low pass filtering. 
\item Designed and built a plasma diagnostic system called Thomson scattering, requiring hardware/software interfaces, signal fitting, maximum likelihood analysis, and database management.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{KLA-Tencor}{June, 2008 - February, 2010}{Applications Engineer}{Milpitas, CA}
\item Generated analytical reports presenting the defect inspection results of samples from potential customers for the evaluation of our products. 
\item Consulted for more than ten companies worldwide teaching clients how to operate semiconductor defect inspection systems and develop algorithms to detect and classify their defects of interest.
\item Managed customer requests through direct interaction and facilitated product development by working with engineering and marketing teams to fulfill these needs.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Lawrence Livermore National Laboratory}{Summer, 2007 \& Summer, 2010}{Research Intern}{Livermore, CA}
\item Conducted a high-energy Thomson scattering experiment and published the results with a small team.
\item Developed data analysis software for X-ray Thomson scattering experiments with an aim to standardize, improve, and speed-up data analysis processing.  This included curve and Gaussian peak fitting.
\item Designed a high-energy electron spectrometer by developing a 3-D relativistic electron propagation computer simulation using the Runge-Kutta method for determining electron trajectories through a magnetic field.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Computer Languages & Python, HTML, CSS\\
Other Computer Skills & Unix, Hadoop, Git, GitHub, LaTeX, MATLAB \\
Basic Knowledge & Spark, SQL, C, JavaScript, D3.js
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Data Science Project Experience}

For additional project details, see \url{www.chrisstoafer.com/projects.html}

\begin{rSubsection}{Urban Health Repository Systems}{Columbia University's SIPA Dean's Challenge}{\url{www.columbia.edu/~ccs2142/uhrs/visuals.html}}{Semi-Finalists}
\item	Effectively collaborated in a team of 6 members to build a data-driven startup with a mission of educating Asthma sufferers about harmful environmental exposures, such as building materials and air quality.
%\item	Our group became semi-finalists in The Columbia SIPA Dean's Challenge.
\item	Served as the technology leader; created interactive web data visualizations, using D3.js and Python, to increase public awareness and understanding of potential factors in Asthma exacerbations.
\end{rSubsection}

\begin{rSubsection}{Bitquant}{Hackbit: Bitcoin Student Hackathon}{\url{www.github.com/cstoafer/bitquant}}{Third place in competition}
\item	Developed an algorithm and script to automatically buy and sell Bitcoin on the Bitstamp market based on the real-time order book, using the Bitstamp API and Python.
\end{rSubsection}

\end{rSection}




%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Leadership and Extracurricular Experience}

\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }

{\bf Columbia Data Science Society}, 2014 - 2015 \\
{\em Website Development Lead}\\
{\em Event coordinator for interfacing the student organization with industry, e.g. career panels and networking.}\\
{\bf Graduate Student Liaison}, 2010 - 2015 \\
{\em Organize social events in my graduate school department to promote faculty and student interactions.} \\
{\bf New York Academy of Science}, 2011 - 2012 \\
{\em STEM Mentor - coached after-school activities in robotics to a group of 20 middle school students.}\\
{\bf Alpha Chi Sigma (Professional Chemistry Fraternity)}, 2005 - 2008 \\
{\em Vice-President, 2006-2007, President, 2007-2008}\\
{\em Increased active enrollment from 30 to 70 members through recruitment and promoting member activity}\\ {\em with interactive events, such as community science fairs and outreach.}\\
{\bf Player on Columbia Men's Hockey Team} \\
{\bf Second degree black belt in Tae Kwon Do}

\end{tabular}

%\begin{rSubsection}{Columbia Data Science Society}{2014 - Present}{Website Development Lead}{}
%\end{rSubsection}
%
%\begin{rSubsection}{Alpha Chi Sigma (Professional Chemistry Fraternity)}{2005 - 2008}{Vice-President, 2006-2007, President, 2007-2008}{}
%%\item Grew campus and community involvement of the club including: science fairs, chemistry workshops for K-12, science awareness, fundraising, and community service.
%
%\end{rSubsection}

\end{rSection}





%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors and Awards}

Capital One Labs Building Block Award for work on text mining toolkit\\
Cal Poly Dean's list and President's list\\
Physical chemistry student of the year, 2007\\
Analytical chemistry student of the year, 2008\\
Golden Key Honour Society member\\
National Society of Collegiate Scholars (NSCS) member

%\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
%
%
%\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------

\end{document}
